Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-30 main.tex
stab at stack protection as L-S NI; don't see story for integrity

Given a machine state $\mach$ and a contour $\contour$, a {\em
  variant} of $\mach$ with respect to $\contour$ is any machine state
$\mach'$ whose components agree with $\mach$ on all components marked
$\VIS$ by $\contour$---i.e., if $\contour(\component) = \VIS$, then
$\mach(\component) = \mach'(\component)$.

@@

These properties are essentially orthogonal: we could enforce WBCF without LSE, and variants of
LSE could apply to control constructs beyond simple procedure calls (e.g. exceptions, coroutines, threads, monitors, etc.).

In terms of NI....
\apt{Perhaps the NI-like property is just LSE, but it holds only if WBCF holds?}

>>>>

Given a machine state $\mach$ and a contour $\contour$, a {\em
  variant} of $\mach$ with respect to $\contour$ is any machine state
$\mach'$ whose components agree with $\mach$ on all components marked
$\VIS$ by $\contour$---i.e., if $\contour(\component) = \VIS$, then
$\mach(\component) = \mach'(\component)$.
\apt{Um..this seems to conflate visibility (\VIS,\HID) with
  security/privacy level (\HIGH,\LOW).  Don't we want to distinguish these?}

@@

These properties are essentially orthogonal: one can certainly have WBCF without LSE, and variants of
LSE could apply to control constructs beyond simple procedure calls (e.g. exceptions, coroutines, threads, monitors, etc.).

Under the assumption that WBCF holds, we can describe LSE as an instance of Lockstep-Noninterference, where the contour at
each step maps the current stack frame to \VIS\ and the remainder of the stack to \HID\. 
The observations on which noninterference is defined will (necessarily)  be made on the values in the current stack frame.
\apt{Again, we're conflating \VIS\ vs. \HID\ with \LOW\ vs \HIGH\; should probably be teased apart.}
LSE has two aspects: secrecy (callees cannot read caller variables) and integrity (callees cannot alter caller variables).
Secrecy is enforced by the variant-closure clause of L-N: since caller data is \HID, changing it cannot alter
the callee's observable behavior.  Integrity is enforced why??? \apt{I've lost confidence that it is.}
